On the probability of finding a nonphysical solution through shadowing

### 2020-10-30 main.tex
Final edits

We have only seen quasi-physical solutions for the tent map.
It is difficult to analytically construct quasi-physical solutions
to the Lorenz equation and other, more complex, governing
equations which typically produce chaotic solutions.  Neverthless, the similarity 
between the tent map and the Lorenz map \cite{tent2}, shown in Figure \ref{fig:lorenz_map}, suggests that
quasi-physical solutions may exist for the Lorenz map, and by
extension, the Lorenz equation.  It is then natural to conjecture
that such aperiodic, nonphysical, quasi-physical solutions
exist in general for chaotic dynamical systems.

@@

\subsection{Are general shadowing solutions physical?}
\label{sec:tentPerts}
In the previous subsection, we examined a tilting perturbation to the tent map.
We derived the fractal conjugacy map, and showed that a typical shadowing trajectory
is exactly the quasi-physical solution we analyzed in section \ref{sec:quasiphysical}.
This example contrasts with section \ref{sec:sub:shadow-example}, in which the
shadowing solutions of a different perturbation, the scaling perturbation,
are physical solutions.  Which situation is more typical?  When we make other
types of perturbations, do we expect to observe physical or nonphysical
shadowing solutions?

%%
%%\begin{figure}[H]
%%    \centering
%%    \includegraphics[width=0.48\textwidth]{figure/tent_tilted_shadow_density_0.01.png}
%%    \hspace{0.02\textwidth}
%%    \includegraphics[width=0.48\textwidth]{figure/tent_tilted_shadow_density_0.05.png}
%%    \\ \vspace{0.02\textwidth}
%%    \includegraphics[width=0.48\textwidth]{figure/tent_tilted_shadow_density_0.4.png}
%%    \hspace{0.02\textwidth}
%%    \includegraphics[width=0.48\textwidth]{figure/tent_tilted_shadow_density_0.7.png}
%%    \caption{Caption}
%%    \label{fig:tent_tilted_shadow}
%%\end{figure}
%%

@@

This section attempts to answer this question by investigating several other
perturbations, the first of which scales the height, but not the width,
of the tent map.  The resulting ``squashed'' tent map, illustrated
in Figure \ref{fig:tent_squashed}, has the closed form 
\begin{equation} \label{eqn:tent_squashed}
\hat{\varphi}^{\rm sq}_s(x) := \begin{cases}
    (2-s)x \quad & x < 1 \\
    (2-s)(2 - x) \quad & x \ge 1
    \end{cases}
\end{equation}

\begin{figure}
    \centering
    \includegraphics[width=0.48\textwidth]{tent_squashed_shadow_density_0.01.png}
    \hspace{0.02\textwidth}
    \includegraphics[width=0.48\textwidth]{tent_squashed_physical_density_0.01.png}
    \\ \vspace{0.02\textwidth}
    \includegraphics[width=0.48\textwidth]{tent_squashed_shadow_density_0.2.png}
    \hspace{0.02\textwidth}
    \includegraphics[width=0.48\textwidth]{tent_squashed_physical_density_0.2.png}
    \caption{The left column shows the empirical probability distribution of the shadowing solution for the squashed tent map at $s=0.01$ (top) and at $s=0.2$ (bottom). The right column shows the empirical probability distribution of a physical solution at the same two values of $s = 0.01$ (top) and $s = 0.2$ (bottom).}
    \label{fig:tent_squashed_shadow}
\end{figure}
In Figure \ref{fig:tent_squashed_shadow}, we show side-by-side the probability distributions generated by observing a long solution (of length 10 billion) 
of $\hat{\varphi}^{\rm sq}_s$ (left) and its corresponding shadowing solution (right)
at two different values of $s.$ The left column showing the probability distribution of the shadowing solution is reminiscent of the hairy probability distributions of 
the quasi-solutions of the tent map in section \ref{sec:quasiphysical}. The reader is referred to the Supplementary Material section \ref{sec:computingShadowing} for a note on the computation of the shadowing solution. Note that, unlike the tilted tent maps, the family of squashed tent maps do not have the uniform distribution as their SRB distribution, as indicated on the right column. However, the SRB distributions are not fractal. That is, the physical solutions of the squashed tent map are distributed according to a regular probability density (right column of Figure \ref{fig:tent_squashed_shadow}). But the shadowing solution, which is a true orbit of the original tent map, is distributed neither like a physical solution of the original tent map nor of the squashed tent map, as suggested by its fractal-like probability distribution.

@@

Again, at $s=0$, the original tent map is recovered, and other values of $s,$ the tent map is ``pinched'' by perturbations that are symmetric around $x = 1$, and zero at the end points. Figure \ref{fig:tent_pinched} shows the pinched tent map at different $s$ values.  

@@

    \caption{The pinched tent map (Eq. \ref{eqn:tent_pinched}) for $s = 0.01, 0.05, 0.2,$ and 0.5.}

@@

can see that the pinching perturbation changes the uniform density of the original tent map to a linearly varying density. The more pronounced the perturbation -- the higher the value of $s$ -- the steeper decline in the density from left to the right. The shadowing distribution, in this case as well, appears fractal. Once again, with probability one -- or, for any randomly chosen initial condition of the solution of the pinched tent map -- any physical solution is shadowed by a quasi-physical solution.

@@

has a corresponding shadowing solution, that is nonphysical. In this section,

@@

A closed form approximation is constructed by regression performed using long solutions 
of the Lorenz map (Figure \ref{fig:lorenz_map}). 
\begin{figure}
    \centering
    \includegraphics[width=0.32\textwidth]{lorenz_zmax_sigma.png}
    \hspace{0.005\textwidth}
    \includegraphics[width=0.32\textwidth]{lorenz_zmax_rho.png}
    \hspace{0.005\textwidth}
    \includegraphics[width=0.32\textwidth]{lorenz_zmax_beta.png}
    \caption{
The left, center, and right plots show the effect of the
    parameters $\sigma, \rho$, and $\beta$ on the Lorenz map, respectively.
    In the left plot, the blue and orange lines represent
    $\sigma=10$ and $12$, respectively, while $\rho  = 28$ and $\beta = 8/3.$
    In the center plot, the blue and orange lines represent
    $\rho=28$ and $30$, respectively, while $\sigma = 10$ and $\beta  = 8/3.$ 
    In the right plot, the blue and orange lines represent
    $\sigma=8/3$ and $10/3$ respectively, while $\sigma = 10$ and 
		$\rho = 28.$}
    \label{fig:lorenz_params}
\end{figure}
\begin{comment}
Is the green line overlapping one of the two lines?
\end{comment}
The Lorenz map approximation obtained this way is illustrated in Figure \ref{fig:lorenz_params}, for variations of the parameters around their standard values of 
$\rho = 28, \sigma = 10,$ and $\beta = 8/3.$ Using the approximate Lorenz map, we calculate next the shadowing solutions. 
\begin{figure}
    \centering
    \includegraphics[width=0.48\textwidth]{lorenz_shadow_density_lorenz_zmax_15_28_2.67.json.png}
    \hspace{0.005\textwidth}
    \includegraphics[width=0.48\textwidth]{baseline_density_lorenz_zmax_15_28_2.67.json.png}
    \\
    \includegraphics[width=0.48\textwidth]{lorenz_shadow_density_lorenz_zmax_10_30_2.67.json.png}
    \hspace{0.005\textwidth}
    \includegraphics[width=0.48\textwidth]{baseline_density_lorenz_zmax_10_30_2.67.json.png}
    \\
    \includegraphics[width=0.48\textwidth]{lorenz_shadow_density_lorenz_zmax_10_28_3.33.json.png}
    \hspace{0.005\textwidth}
    \includegraphics[width=0.48\textwidth]{baseline_density_lorenz_zmax_10_28_3.33.json.png}
    \caption{The left column shows the empirical distribution of the shadowing solution, and the right column shows the physical distribution of the Lorenz map at the following sets of parameters: top row: $\sigma = 15, \rho = 28, \beta = 8/3$, $\rho = 29$, middle row: $\sigma = 10, \rho = 30, \beta = 10/3$, and bottom row: $\sigma = 10, \rho = 28, \beta = 10/3$.
    }
    \label{fig:lorenz_params_scaled}
\end{figure}
The empirical distribution computed from long shadowing solutions, of length 10 billion, are shown in the left column of Figure \ref{fig:lorenz_params_scaled} at three different sets of parameter values, which are also different from the standard values of $\rho = 28, \sigma = 10$, and $\beta = 8/3$. 
In each row, one of the parameters is  $\rho = 29$ and $\rho = 30$ are used, respectivel, while the other two parameters are retained at their standard values. In the bottom row, only the parameter $\beta$ is perturbed from the standard values; $\beta = 10/3$ is used. On the right column, we plot the distribution of physical solutions, the SRB distribution, at the set of parameters corresponding to each row. We again notice that, while the physical distributions appear smooth, the shadowing solutions clearly exhibit roughness. Thus, we draw the same conclusion in the Lorenz map as in the various perturbations of the tent map treated in section \ref{sec:tentPerts}: shadowing solutions do not have the same distribution as a typically observed solution of the governing equation. In other words, shadowing solutions are nonphysical.

>>>>

We have only seen quasi-physical solutions for the tent map.
It is difficult to analytically construct quasi-physical solutions
to the Lorenz equation and other, more complex, governing
equations which typically produce chaotic solutions.  Nevertheless, the similarity 
between the tent map and the Lorenz map \cite{tent2}, shown in Figure \ref{fig:lorenz_map}, suggests that
quasi-physical solutions may exist for the Lorenz map, and by
extension, the Lorenz equation.  It is then natural to conjecture
that such aperiodic, nonphysical, quasi-physical solutions
exist in general for chaotic dynamical systems.

@@

\subsection{Are general shadowing solutions physical?}
\label{sec:tentPerts}
In the previous subsection, we examined a tilting perturbation to the tent map.
We derived the fractal conjugacy map, and showed that a typical shadowing trajectory
is exactly the quasi-physical solution we analyzed in section \ref{sec:quasiphysical}.
This example contrasts with section \ref{sec:sub:shadow-example}, in which the
shadowing solutions of a different perturbation, the scaling perturbation,
are physical solutions.  Which situation is more typical?  When we make other
types of perturbations, do we expect to observe physical or nonphysical
shadowing solutions?
%%
%%\begin{figure}[H]
%%    \centering
%%    \includegraphics[width=0.48\textwidth]{figure/tent_tilted_shadow_density_0.01.png}
%%    \hspace{0.02\textwidth}
%%    \includegraphics[width=0.48\textwidth]{figure/tent_tilted_shadow_density_0.05.png}
%%    \\ \vspace{0.02\textwidth}
%%    \includegraphics[width=0.48\textwidth]{figure/tent_tilted_shadow_density_0.4.png}
%%    \hspace{0.02\textwidth}
%%    \includegraphics[width=0.48\textwidth]{figure/tent_tilted_shadow_density_0.7.png}
%%    \caption{Caption}
%%    \label{fig:tent_tilted_shadow}
%%\end{figure}
%%

@@

This section attempts to answer this question by investigating several other
perturbations, the first of which scales the height, but not the width,
of the tent map.  The resulting ``squashed'' tent map, illustrated
in Figure \ref{fig:tent_squashed}, has the closed form 
\begin{equation} \label{eqn:tent_squashed}
\hat{\varphi}^{\rm sq}_s(x) := \begin{cases}
    (2-s)x \quad & x < 1 \\
    (2-s)(2 - x) \quad & 2 >  x \ge 1.
    \end{cases}
\end{equation}

\begin{figure}
    \centering
    \includegraphics[width=0.48\textwidth]{tent_squashed_shadow_density_0.01.png}
    \hspace{0.02\textwidth}
    \includegraphics[width=0.48\textwidth]{tent_squashed_physical_density_0.01.png}
    \\ \vspace{0.02\textwidth}
    \includegraphics[width=0.48\textwidth]{tent_squashed_shadow_density_0.2.png}
    \hspace{0.02\textwidth}
    \includegraphics[width=0.48\textwidth]{tent_squashed_physical_density_0.2.png}
    \caption{The left column shows the empirical probability distribution of the shadowing solution for the squashed tent map at $s=0.01$ (top) and at $s=0.2$ (bottom). The right column shows the empirical probability distribution of a physical solution at the same two values of $s = 0.01$ (top) and $s = 0.2$ (bottom).}
    \label{fig:tent_squashed_shadow}
\end{figure}
In Figure \ref{fig:tent_squashed_shadow}, we show side-by-side the probability distributions generated by observing a long solution (of length 10 billion) 
of $\hat{\varphi}^{\rm sq}_s$ (left) and its corresponding shadowing solution (right)
at two different values of $s.$ The left column showing the probability distribution of the shadowing solution is reminiscent of the hairy probability distributions of 
the quasi-solutions of the tent map in section \ref{sec:quasiphysical}. The reader is referred to the Supplementary Material section \ref{sec:computingShadowing} for the computational method used in this paper, for the shadowing solutions. Note that, unlike the tilted tent maps, the family of squashed tent maps do not have the uniform distribution as their SRB distribution, but have a different regular probability distribution as indicated on the right column of Figure \ref{fig:tent_squashed_shadow}. On the other hand, the shadowing solution is distributed neither like a physical solution of the original tent map nor of the squashed tent map, as suggested by its fractal-like probability distribution on the left column of Figure \ref{fig:tent_squashed_shadow}.

@@

Again, at $s=0$, the original tent map is recovered, and at other values of $s,$ the tent map is ``pinched'' by perturbations that are symmetric around $x = 1$, and zero at the end points. Figure \ref{fig:tent_pinched} shows the pinched tent map at different $s$ values.  

@@

    \caption{The pinched tent map (Eq. \ref{eqn:tent_pinched}) for $s = 0.01$ (blue), $s=0.05$ (orange), $s=0.2,$ (green) and $s=0.5$(red).}

@@

can see that the pinching perturbation changes the uniform density of the original tent map to a linearly varying density. The more pronounced the perturbation -- the higher the value of $s$ -- the steeper the slope. The shadowing distribution, in this case as well, appears fractal. Once again, with probability one -- or, for any randomly chosen initial condition of the solution of the pinched tent map -- a physical solution is shadowed by a quasi-physical solution.

@@

has a corresponding shadowing solution that is nonphysical. In this section,

@@

A closed form approximation is constructed by regression performed using long solutions 
of the Lorenz map (Figure \ref{fig:lorenz_map}). 
\begin{figure}
    \centering
    \includegraphics[width=0.32\textwidth]{lorenz_zmax_sigma.png}
    \hspace{0.005\textwidth}
    \includegraphics[width=0.32\textwidth]{lorenz_zmax_rho.png}
    \hspace{0.005\textwidth}
    \includegraphics[width=0.32\textwidth]{lorenz_zmax_beta.png}
    \caption{
The left, center, and right plots show the effect of the
    parameters $\sigma, \rho$, and $\beta$ on the Lorenz map, respectively.
    In the left plot, the blue and orange lines represent
    $\sigma=10$ and $12$, respectively, while $\rho  = 28$ and $\beta = 8/3.$
    In the center plot, the blue and orange lines represent
    $\rho=28$ and $30$, respectively, while $\sigma = 10$ and $\beta  = 8/3.$ 
    In the right plot, the blue and orange lines represent
    $\sigma=8/3$ and $10/3$ respectively, while $\sigma = 10$ and 
		$\rho = 28.$}
    \label{fig:lorenz_params}
\end{figure}
\begin{comment}
Is the green line overlapping one of the two lines?
\end{comment}
The Lorenz map approximation obtained this way is illustrated in Figure \ref{fig:lorenz_params}, for variations of the parameters around their standard values of 
$\rho = 28, \sigma = 10,$ and $\beta = 8/3.$ Using the approximate Lorenz map, we calculate next the shadowing solutions. 
\begin{figure}
    \centering
    \includegraphics[width=0.48\textwidth]{lorenz_shadow_density_lorenz_zmax_15_28_2.67.json.png}
    \hspace{0.005\textwidth}
    \includegraphics[width=0.48\textwidth]{baseline_density_lorenz_zmax_15_28_2.67.json.png}
    \\
    \includegraphics[width=0.48\textwidth]{lorenz_shadow_density_lorenz_zmax_10_30_2.67.json.png}
    \hspace{0.005\textwidth}
    \includegraphics[width=0.48\textwidth]{baseline_density_lorenz_zmax_10_30_2.67.json.png}
    \\
    \includegraphics[width=0.48\textwidth]{lorenz_shadow_density_lorenz_zmax_10_28_3.33.json.png}
    \hspace{0.005\textwidth}
    \includegraphics[width=0.48\textwidth]{baseline_density_lorenz_zmax_10_28_3.33.json.png}
    \caption{The left column shows the empirical distribution of the shadowing solution, and the right column shows the physical distribution of the Lorenz map at the following sets of parameters: top row: $\sigma = 15, \rho = 28, \beta = 8/3$, $\rho = 29$, middle row: $\sigma = 10, \rho = 30, \beta = 10/3$, and bottom row: $\sigma = 10, \rho = 28, \beta = 10/3$.
    }
    \label{fig:lorenz_params_scaled}
\end{figure}
The empirical distribution computed from long shadowing solutions, of length 10 billion, are shown in the left column of Figure \ref{fig:lorenz_params_scaled} at three different sets of parameter values, which are also different from the standard values of $\rho = 28, \sigma = 10$, and $\beta = 8/3$. 
In each row, one of the parameters is perturbed from the standard values. On the right column, we plot the distribution of physical solutions, the SRB distribution, at the set of parameters corresponding to each row. We again notice that, while the physical distributions appear smooth, the shadowing solutions clearly exhibit roughness. Thus, we draw the same conclusion in the Lorenz map as in the various perturbations of the tent map treated in section \ref{sec:tentPerts}: shadowing solutions do not have the same distribution as a typically observed solution of the governing equation. In other words, shadowing solutions are nonphysical.
